---
title: "ASSIGNEMENT 5"
author: "BIDHATA SUBBA"
date: "11/22/2016"
output: html_document
---

# 1. Describe the distribution of score. Is the distribution skewed? What does that tell you about how students rate courses? Is this what you expected to see? Why, or why not?

#1 answer:

```{r}
hist(evals$score)

# Yes, the distribution is skewed. Students rated maximum positive than negative for their professors in this evaluation. No,we did not expect this to see because we had expected to see normal distribution where most professors would rated average and very few would be rated extremly excellent or unsatifactry.
```


#2. Excluding score, select two other variables and describe their relationship using an appropriate visualization (scatterplot or side-by-side boxplots).

```{r}
boxplot(evals$bty_avg ~ evals$age)
#It shows tha female are rated higer than male.
```


#Multiple Linear Regression
```{r}
plot ( evals $ bty_avg  ~  evals $ bty_f1lower )
cor ( evals $ bty_avg ,  evals $ bty_f1lower )
```
```{r}
plot(evals[, 13:19])
```

#3. Is bty_avg still a significant predictor of score? Has the addition of gender to the model changed the parameter estimate for bty_avg?
```{r}
summary(lm(evals$score ~ evals$bty_avg))

#There is not so much change is the parameter.
```

#4. What is the equation of the line corresponding to males? (Hint: For males, the parameter estimate is multiplied by 1.) For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?
```{r}

#highest beauty for male and female is 7.833. Average score for male is 5 and female is 4.8 from the dataset.
```

#5. Create a new model called m_bty_rank with gender removed and rank added in. How does R appear to handle categorical variables that have more than two levels? Note that the rank variable has three levels: teaching, tenure track, tenured.
```{r}
m_bty_rank = lm(score ~ bty_avg + rank, data = evals)
summary(m_bty_rank)
```
```{r}
names(m_bty_rank)
```

#6. The interpretation of the coefficients in multiple regression is slightly different from that of simple regression. The estimate for bty_avg reflects how much higher a group of professors is expected to score if they have a beauty rating that is one point higher w hile holding all other variables constant. In this case, that translates into considering only professors of the same rank with bty_avg scores that are one point apart.
```{r}

```
#7. Which variable would you expect to have the highest p-value in this model? Why? Hint: Think about which variable would you expect to not have any association with the professor score.
```{r}
m_full <- lm ( score ~ rank + ethnicity +
gender + language + age + cls_perc_eval + cls_students + cls_level + cls_profs + cls_credits + bty_avg + pic_outfit + pic_color , data = evals )
summary ( m_full )

#cls_creditsone credit has the highest P-value because “number of professors” cls_profs as the variable to have the least assoication with the professor’s evaluation score.
```

#8. Check your suspicions from the previous exercise. Include the model output in your response.
```{r}
plot(evals$score ~ evals$cls_profs)
# Yes, it has the highest p-value in the model. The = “number professors” which has the least association to “scores”. 
```

#9. Interpret the coefficient associated with the ethnicity variable.
```{r}
m_full = lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval + cls_students + cls_level + cls_profs + cls_credits + bty_avg + pic_outfit + pic_color, data = evals)
summary(m_full)
# Coefficient= 0.1234929 is positive, which means professors score goes up when they are ‘1’, or not a minority.
```

#10. Drop the variable with the highest p-value and refit the model. Did the coefficients and significance of the other explanatory variables change? (One of the things that makes multiple regression interesting is that coefficient estimates depend on the other variables that are included in the model.) If not, what does this say about whether or not the dropped variable was collinear with the other explanatory variables?

```{r}
m_drop = lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval + cls_students + cls_level + cls_credits + bty_avg + pic_outfit + pic_color, data = evals)

summary(m_drop)
# Yes,they the variables change.which  means there was a collinear relationship between cls_profs single and the other variables - or else getting rid of it wouldn’t have affected the other coefficients.
```

#11. Using backward-selection and p-value as the selection criterion, determine the best model. You do not need to show all steps in your answer, just the output for the final model. Also, write out the linear model for predicting score based on the final model you settle on.
```{r}
m_drop7 = lm(score ~ ethnicity + gender + language + age + cls_perc_eval + cls_credits + bty_avg + pic_color, data = evals)

summary(m_drop7)

# score = 3.907030 + (0.163818)ethnicity + (0.202597)gender + (-0.202597)language + (-.0006925)age + (0.006925)cls_perc_eval + (0.517205)cls_credits + (0.046732)bty_avg + (-0.113939)pic_outfit + (-0.180870)pic_color
```


#12. Verify that the conditions for this model are reasonable using diagnostic plots.

```{r}
plot(m_drop7$residuals ~ evals$score)
abline(h = 0, lty = 3)
```
```{r}
hist(m_drop7$residuals)
```
```{r}
qqnorm(m_drop7$residuals)
qqline(m_drop7$residuals)
```


