---
title: "BS"
author: "BS"
date: "October 9, 2016"
output: pdf_document
---

a. For each of the following commands, either explain why they should be errors, or explain the
non-erroneous result.
vector1 <- c("5", "12", "7", "32")
max(vector1)
sort(vector1)
sum(vector1)

Ans)
Character quantities and character vectors are used frequently in R, for example as plot labels. Where needed they are denoted by a sequence of characters delimited by the double quote character, e.g., "x-values"

```{r}

vector1 <- c(5,12,7,32)
max(vector1)
sort(vector1)
sum(vector1)

```
2)For the next series of commands, either explain their results, or why they should produce errors.
Ans)
```{r}
vector1 <- c(5, 12, 7, 32)
vector2 <- c(5,7,12)
vector2[2] + vector2[3]
```

```{r}
dataframe3 <- data.frame(z1=5,z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]
```

```{r}
list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
```

2)mtcars, another dataset under the datasets library in R, was extracted from the 1974 Motor Trend
US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for
32 automobiles (1973-74 models). Note: Although both are about cars, mtcars is a di!erent dataset
than the mpg dataset we worked with in the class.
a. What is the type of mtcars? Also is it a data frame? 
Ans- Its a "list" type of dataset. YES, mtcars is a data frame.
b. How many rows and columns does mtcars have?
```{r}
nrow(mtcars)
data(mtcars)
ncol(mtcars)
```
c. What are the names of the columns of mtcars?
```{r}
require(graphics)
pairs(mtcars, main = "mtcars data")
coplot(mpg ~ disp | as.factor(cyl), data = mtcars, panel = panel.smooth, rows = 1)
```
d. What is the value of row 5, column 7 of mtcars? What does the value signify ?
ans)
The column 7 in the dataset mtcars is "qsec" and the row 5 is "Hornet Sportabout". The value is the result of matrix matcars.
```{r}
mtcars[5,7]
```
e. Display the second row of mtcars in its entirety.
```{r}
mtcars[2,]
```
f. Explain what this command does by running it on your data and examining the object.
```{r}
mydata<- mtcars
names(mydata) <- c("mileage","cylinder",seq(0,8))
names(mydata)                   
```
g.  
h.
```{r}
mtcars <- within(mtcars, {disp_l <- disp*0.0163871})
mtcars <- within(mtcars,{hp_l <- hp/disp_l})
rownames(mtcars) [which.max(mtcars[,13])]
```

3.
```{r}
seq(0,10000,by=372)
seq(0,10000,length.out = 50)
rep(1:3, times=3)
rep(1:3, each=3)
```

Part II - Descriptive Stats

TRUE !! My instructor likes cars a lot.
```{r}
library(MASS)
data("Cars93")
View(Cars93)
summary(Cars93)
nrow(Cars93)
Rear_T = subset(Cars93, DriveTrain=='Rear')
mean(Rear_T[,5])
median(Rear_T[,5])
sd(Rear_T[,5])
Seven.seater = subset(Cars93, Passengers =="7")
min(Seven.seater [,13])
Atleastsix.seater = subset(Cars93, Passengers >="6")
min(Atleastsix.seater[,13])
```
